ranacapa: An R package to explore environmental DNA data with exploratory statistics and interactive visualizations

### 2018-10-02 manuscript.Rmd
moves figures, ms has some comments

#### Figure 2
```{r, fig.cap="Figure 2: Taxonomy heatmap as shown in the `ranacapa` Shiny app. Taxonomy is shown at the Order level in this figure; in the app, users can choose the taxonomic level to show in the heatmap."}
fig2
```

@@

#### Figure 3
```{r, fig.cap="Figure 3: Taxonomy barplot as shown in the `ranacapa` Shiny app. Taxonomy is shown at the Order level in this figure; in the app, users can choose the taxonomic level to show in the barplot"}
fig3
```

@@

#### Figure 4
```{r, fig.cap="Figure 4: Alpha diveristy boxplots as shown in the `ranacapa` Shiny app. Users can select the X-axis variable using a dropdown menu in the app."}
fig4
```

@@

#### Figure 5
```{r, fig.cap="Figure 5: PCoA ordination of the samples as shown in the `ranacapa` Shiny app. Users can select the grouping variable with a dropdown menu in the app."}
fig5
```

@@

>>>>

@@

@@

@@

@@

## Figures

#### Figure 2
```{r, fig.cap="Figure 2: Taxonomy heatmap as shown in the `ranacapa` Shiny app. Taxonomy is shown at the Order level in this figure; in the app, users can choose the taxonomic level to show in the heatmap."}
fig2
```
#### Figure 3
```{r, fig.cap="Figure 3: Taxonomy barplot as shown in the `ranacapa` Shiny app. Taxonomy is shown at the Order level in this figure; in the app, users can choose the taxonomic level to show in the barplot"}
fig3
```

#### Figure 4
```{r, fig.cap="Figure 4: Alpha diveristy boxplots as shown in the `ranacapa` Shiny app. Users can select the X-axis variable using a dropdown menu in the app."}
fig4
```
#### Figure 5
```{r, fig.cap="Figure 5: PCoA ordination of the samples as shown in the `ranacapa` Shiny app. Users can select the grouping variable with a dropdown menu in the app."}
fig5
```
